\documentclass[margin,line]{resume}
\usepackage[hidelinks]{hyperref}

\begin{document}

\name{Nan Jiang}

\begin{resume}
\section{Contact Information}
\begin{tabular}{@{}p{3.5in}p{3.5in}}
School of Computer Science and Engineering & { E-mail:}  {\tt nanjiang@buaa.edu.cn} \\
Beihang University                         & { Blog:} {\tt jiangnanhugo.github.io/blog} \\
Beijing, China                             & { Github:} {\tt github.com/jiangnanhugo} \\
\end{tabular}


\section{Education}
{\bf Beihang University} (BUAA), Beijing, China \hfill {\bf Sept., 2015 - Mar., 2018}\\
Master in Computer Science. Advisor: \underline{\href{http://dblp.uni-trier.de/pers/hd/r/Rong:Wenge}{Wenge Rong}}.\\
Graduate Design: Exploration of Hierarchical Softmax for Recurrent Language Models. \\
Research Interests: Natural Language Processing, Deep Learning. 

{\bf Zhejiang University of Technology} (ZJUT), Zhejiang, China \hfill {\bf Sept., 2011 - Jul., 2015}\\
Bachelor in Computer Science and Electronic Engineering (double degree). \\
\space Major GPA: 4.0, Top 1 of 296. 


\section{Publications}
\textbf{Nan Jiang}, Wenge Rong, Min Gao, Yikang Shen and Zhang Xiong. Exploration of Tree-based Hierarchical Softmax for Recurrent Language Models[C]. Proceedings of the Twenty-Sixth International Joint Conference on Artificial Intelligence (IJCAI), 2017, pp. 1951-1957. [\href{https://github.com/jiangnanHugo/lmkit}{code}][\href{https://www.ijcai.org/proceedings/2017/0271.pdf}{pdf}]

\textbf{Nan Jiang}, Wenge Rong, Min Gao, Yikang Shen and Zhang Xiong. Exploration of Hierarchical Softmax for Recurrent Language Models[J]. IEEE Transactions on Neural Networks and Learning Systems (TNNLS). (Major Revision)

Yikang Shen, Wenge Rong, \textbf{Nan Jiang}, Baolin Peng, Jie Tang and Zhang Xiong. Word Embedding Based Correlation Model for Question/Answer Matching[C]. Proceedings of the Thirtieth {AAAI} Conference on Artificial Intelligence (AAAI), 2017, pp. 3511-3517.

\textbf{Nan Jiang}, Wenge Rong, Yifan Nie, Yikang Shen and Zhang Xiong. Event Trigger Identification with Noise Contrastive Estimation[J]. IEEE/ACM Transactions on Computational Biology and Bioinformatics, 2017, pp. 1-11. [\href{https://github.com/jiangnanHugo/mlee-nce}{code}][\href{https://github.com/jiangnanhugo/paper/blob/master/APBC2017/APBC2017.pdf}{pdf}]

\textbf{Nan Jiang}, Wenge Rong, Baolin Peng, Yifan Nie and Zhang Xiong. Modeling Joint Representation with Tri-Modal DBNs for Query and Question Matching[J]. IEICE Transactions on Information and Systems, 2016, 99(4): 927-935.

\textbf{Nan Jiang}, Wenge Rong, Baolin Peng, Yifan Nie and Zhang Xiong. An Empirical Analysis of Different Sparse Penalties
for Autoencoder in Unsupervised Feature Learning[C]. International Joint Conference on Neural Networks (IJCNN), 2015, pp. 1-8.




\section{Experiences}
{\bf Search Technology Center Asia, Microsoft} \hfill { Beijing, China}

{ Natural Language Processing Intern, Manager: \underline{\href{http://dblp.uni-trier.de/pers/hd/z/Zhou:Li}{Li Zhou}}} \hfill {\bf Dec., 2016 - Sept., 2017}\\
- Clean crawled conversations with regular expression from Reddit;\\
- Investigate current methods to improve neural conversation model;\\
- Attend competitions on Kaggle and contribute different deep models for the tasks.




{\bf Youdao, Netease}  \hfill { Beijing, China}

{ Machine Translation Intern, Manager: \underline{\href{http://dblp.uni-trier.de/pers/hd/d/Duan:Yitao}{Yitao Duan}}} \hfill {\bf Jun, 2016 - Dec., 2016}\\
- Investigate recent advances in language models; \\
- Implement optimizations for RNNLM with large vocabulary; \\
- Tune the neural machine translation model for online usage.


%{\bf Engineering Research Center}, Beihang University
%
%{\em Research Assistant} \hfill {\bf Sept., 2015 - June, 2016}\\
%Learn the basic theory on DL and implement diverse models on deeplearning.net. Besides, applying these algorithms on semantic analysis and language model.




\section{Selected \\ Awards}

National Scholarship, BUAA \hfill {10/303, 2017}\\
Quora Question Pairs, Kaggle \hfill {$8^{th}$/3307, 2017} 

Highway Tollgates Traffic Flow Prediction, KDD CUP  \hfill {$3^{rd}$/386, 2017}

Travel Grant of IEEE on IJCNN Conference, IEEE Society \hfill { 2015}

Excellent Graduation Paper, ZJUT \hfill {10/296, 2015}

Outstanding Graduate Student, ZJUT\hfill {10/296, 2015}

%2012 $\to$ 2014, Zhejiang University of Technology, The First Prize Scholarship

National Scholarship, ZJUT \hfill {2/296, 2011}




\section{ Skills}
\begin{tabular}{@{}p{3.2in}p{4in}}
Programming: C/C++, Python, Java, Matlab;& Tools: Git, Markdown, Bash; \\
Libraries: Theano, Lasagne, Tensorflow;  & Language: Chinese (native), English (fluent). 
\end{tabular}

%\section{Activities}
%Attend the IJCNN2015, APBC2017, AAAI2017, IJCAI2017 conference;\\
%Review paper for IEEE Access.

\section{Unpublished Papers}
%Sequence Generation with augmented Multi-step Loss. \\
Vocabulary Factorized Optimization for Recurrent Language Model. (Under review at AAAI2018)
Addressing Universal Replies in Response Generation Models with Marginal Regularization (Under review at WWW2018)\\

\end{resume}
\end{document}




